%!TEX root = ../thesis.tex

% *****************************************************************************
% ******************************** INTRODUCTION *******************************
% *****************************************************************************

\chapter*{Introduction}

In the domain of industrial automation, Datasensing emerges as a key player, specializing in the development, manufacturing, and supply of advanced solutions in Machine Vision, Sensors, and Safety systems.
Their extensive product line includes smart cameras, industrial cameras, industrial vision processors, software, and accessories for Machine Vision, as well as a range of sensors and safety features like light curtains, laser scanners, and control units. Focused on industrial automation, Datasensing offers services in different sectors, including automotive, electronics, food and beverage, pharmaceuticals, general manufacturing, and intralogistics.

This thesis centers around the development and implementation of a Pub/Sub (Publish/Subscribe) communication platform specifically designed for embedded systems. Within the context of Datasensing's expertise in automation, safety, and machine vision, the research aims to contribute to the advancement of communication paradigms within this specialized field.
The primary goal is to design a Pub/Sub middleware that addresses the unique requirements of embedded systems in the automation industry, providing a robust and efficient platform for facilitating seamless information exchange among heterogeneous processors of embedded devices.

To achieve the goal of the project, the thesis is structured to provide a comprehensive exploration of embedded systems, focusing on the analysis of specific characteristics of the chosen embedded board and a detailed study of the platform Apache Kafka as a solution for publish/subscribe (Pub/Sub) communication.
The last chapter of the thesis goes into the design and implementation of a Pub/Sub platform customized for embedded systems, incorporating insights gained from the analysis of both the embedded board and Apache Kafka.
The conclusive section presents the experimental results, providing an evaluation of the proposed Pub/Sub platform's performance and effectiveness within the domain of embedded systems.
